Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-03-10 paper/tex/methods.tex
edited TPZ

Trees for \Pz \citep[\tpz\footnote{\url{https://github.com/mgckind/MLZ}},][]{Carrasco_Kind:13,Carrascokind:14} is a parallel machine learning algorithm that generates photometric redshift PDFs using prediction trees and random forest techniques.
The code recursively splits the input data (i.~e.~the training sample), into two branches, one after another, until a terminal leaf is created that meets a termination criterion (e.~g.~a minimum leaf size or a variance threshold).
Bootstrap samples from the training data and associated errors are used to build a set of prediction trees.
In order to minimize correlation between the trees, the data is divided in such a way that the highest information gain among the random subsample of features is obtained at every point.
The regions in each terminal leaf node corresponds to a specific subsample of the entire data that possesses similar properties.

The training data is examined before running TPZ.
Since TPZ does not handle non-detections (magnitudes flagged as 99.0), we replace these values with an approximation of the $1\sigma$ detection threshold, i.~e.~a signal to noise ratio of 1 in terms of magnitude uncertainty using the equation $dm = 2.5 ~ \log ( 1 + N/S )$ where $dm \sim 0.7526 ~ mag$ for $N/S=1$.
That is, for each band, we replace the non-detection with the magnitude corresponding to the error of 0.7526 from the error model forecasted for 10-year LSST data.
The Out-of-Bag \citep{Breiman:84,Carrasco_Kind:13} cross-validation technique is used within TPZ to evaluate its predictive validity and determine the relative importance of the different input attributes.
We employed this information to calibrate our algorithm.

In the present work, the LSST magnitudes $u,~g,~r,~i$ and colours $u-g,~g-r,~r-i,~i-z,~z-y$ and their associated errors are used in the process of growing 100 trees with a minimum leaf size of 5 (the $z$ and $y$ magnitudes did not show significant correlation with the redshift in our cross-validation, so we did not use them when constructing our trees).
We partitioned our redshift space into 200 bins and smoothed each individual PDF with a smoothing scale of twice the bin size.
%there was a typo here that had 100 bins, I double checked, it is 200 in the final run.

>>>>

Trees for \Pz \citep[\tpz\footnote{\url{https://github.com/mgckind/MLZ}},][]{Carrasco_Kind:13,Carrascokind:14} uses prediction trees and random forest techniques to estimate \pzpdf s.
\tpz\ recursively splits the training set into branch pairs based on maximizing information gain among a random subsample of features, to minimize correlation between the trees, terminating only when a newly created leaf meets a criterion, such as a leaf size minimum or a variance threshold.
The regions in each terminal leaf node correspond to a subsample of the training set with similar properties.
Bootstrap samples from the training set photometry and errors are used to build a set of prediction trees.

To run \tpz, we replaced nondetections with an approximation of the $1\sigma$ detection threshold based on the error forecast of the 10-year \lsst\ data, i.~e. $dm = 2.5 \log (1 + N/S)$ where $dm \sim 0.7526$ mag for $N/S = 1$.
We calibrated \tpz\ with the Out-of-Bag cross-validation technique \citep{Breiman:84,Carrasco_Kind:13} to evaluate its predictive validity and determine the relative importance of the different input attributes.
We grew 100 trees to a minimum leaf size of 5 using the $ugri$ magnitudes, all $u-g, g-r, r-i, i-z, z-y$ colours, and the associated errors, as the $z$ and $y$ magnitudes did not show significant correlation with the redshift in our cross-validation.
We partitioned our redshift space into 200 bins and smoothed each individual PDF with a smoothing scale of twice the bin size.
